# Results

```{r}
library(tidyverse)
library(patchwork)
library(RColorBrewer)
library(GGally)
library(repr)
library(ggnewscale)
library(Lock5withR)
library(vcd)
library(gridExtra)
library(grid)
library(ggpubr)

```

```{r read_data}
df = read.csv("Speed Dating Data.csv")
```

## Representation of paricipants by different categories

First, let us check the representation of our participants. This answers the question if the sample of students participating in this research experiment is truly randomized. This can help us know if there is/are a group of people that is/are over-represented. In other words, it tells us about the selection bias.

We have chosen four characteristics of the participants: field of study, age, race, and intended career. Here are the bar plots for the same.

*Note: The field, race, and career codes are summarized in the [data key](https://github.com/amruthasundar/final-edav-project/blob/main/Speed%20Dating%20Data%20Key.doc).*

```{r fig.width=12, fig.height=9}
df_by_field = df %>% 
  group_by(field_cd) %>% 
  summarise(count = n()) %>% 
  mutate(per = count*100/sum(count))

df_by_field$field_cd = as.factor(df_by_field$field_cd)

g_by_field = ggplot(df_by_field, aes(x = field_cd, y = per)) +
  geom_bar(stat = "identity", color = "#77D86C", fill = "#B3ECAD", alpha = 0.9) +
  xlab("Field of Study") +
  ylab("Percentage of participants") +
  ggtitle("Representation of participants by field of study")

df_by_age = df %>% 
  group_by(iid) %>% 
  select(iid, age)

df_by_age = unique(df_by_age)

g_by_age = ggplot(df_by_age, aes(x = age)) +
  geom_bar(color = "#77D86C", fill = "#B3ECAD", alpha = 0.9) +
  #scale_x_binned() +
  xlab("Age Group") +
  ylab("Number of participants") +
  ggtitle("Representation of participants by age")

df_by_race = df %>% 
  group_by(iid) %>% 
  select(iid, race)

df_by_race$race = as.factor(df_by_race$race)

g_by_race = ggplot(df_by_race, aes(x = race)) +
  geom_bar(color = "#77D86C", fill = "#B3ECAD", alpha = 0.9, binwidth = 5) +
  xlab("Race") +
  ylab("Number of participants") +
  ggtitle("Representation of participants by race")

df_by_career = df %>% 
  group_by(iid) %>% 
  select(iid, career_c)

df_by_career = unique(df_by_career)
df_by_career$career_c = as.factor(df_by_career$career_c)

g_by_career = ggplot(df_by_career, aes(x = career_c)) +
  geom_bar(color = "#77D86C", fill = "#B3ECAD", alpha = 0.9) +
  xlab("Intended Career") +
  ylab("Number of participants") +
  ggtitle("Representation of participants by intended career")

plot = (g_by_field | g_by_age)/(g_by_race | g_by_career)
plot



```


Here are the inferences from these plots:
  
  **1. For field of study**
  
  We can see that about 23% of the participants are from the 8th field of study, which is Business/Econ/Finance. This represents the highest percentage of students. Considering that this experiment was conducted by professors from the Columbia Business School, a lot of students from that field were expected. This is followed by fields 10 (Biological Sciences/Chemistry/Physics) and 5 (Engineering) representing the 2nd and 3rd highest percentages.

The 17th field of study, which is Architecture, constitutes about less than 1% of the participants. This is the least represented group in terms of field of study. Before that, comes field 12 (undecided), before which comes field 18 (other).

**2. For age group**
  
  We can observe that most students are between the age 20 and 30, with about 68 people with age around 27. Almost all the participants are between 18 and 39 years of age, with the exception of a few of age 42 and 55.

**3. For race**
  
  We can observe that race 2, which is European/Caucasian-American is the highest represented group here, which has about 4700 participants. Second most highest represented race is 4, i.e., Asian/Pacific Islander/Asian-American with about 2000 participants.

The count for race not specified is the least among all the races. Apart from that, the least represented race is Black/African American with about 450 participants.

**4. For intended career**
  
  Here, we can observe that the intended career of most students is career 2 and 7, i.e., Academic/Research and Banking/Consulting/Finance/Marketing/Business/CEO/Entrepreneur/Admin respectively. They constitute for about 155 and 135 participants respectively. The least represented career field is career 17, which is Architecture. Similar trend was seen in the representation by field of study.


## Number of yes matches per participant

In the original experiment, the variable `match` is the target variable. This indicates if the person was matched to the other person or not. We can use a Cleveland dot plot to show the number of yes matches each participant got. As mentioned before, we are using waves 10-21. Moreover, we faceted them by waves and color coded by the gender so we can also understand patterns among genders and within individual waves.

```{r fig.width=12, fig.height=40}
df_match_total = df %>% 
  filter(wave %in% (10:21)) %>% 
  select(iid, match, wave, gender) %>% 
  group_by(iid) %>% 
  mutate(yes = sum(match))

df_match_total = unique(df_match_total)
df_match_total$iid = as.factor(df_match_total$iid)
df_match_total$wave = as.factor(df_match_total$wave)
df_match_total$gender = factor(df_match_total$gender,
                               levels = c(0,1),
                               labels = c("female","male"))
g_match_total = ggplot(df_match_total, aes(x = yes, y = reorder(iid, yes), color = gender)) +
  geom_point(size = 3) +
  scale_x_continuous(limits = c(0, 15), breaks = seq(0, 15, 5)) +
  facet_grid(rows = vars(wave), scales = "free_y", space = "free_y") +
  scale_colour_manual(values = c("#77D86C", "#DD8C75")) +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(colour = "grey60", linetype = "dashed")) +
  xlab("Number of yes matches") +
  ylab("Participant ID number") +
  ggtitle("Number of yes matches per person faceted by wave",
          subtitle = "For waves 10-21 (color-coded by gender)")

g_match_total
```

Here, we can observe that the maximum number of yes matches of participants in waves 10 and 13 is always less than 5. Also, the highest number of matches for waves 20 and 18 is 3. Waves 11, 14, 15, 18 and 21 have a wide variety of matches for different people.

Moreover, all waves have participants who are not matched with other people. The number of participants across all waves who did not get matched seem to have an even number of males and females. The most matched participant is a female from wave 21 who got 14 matches.

## Analysing correlation between the chosen variables

One of the important questions we want to address is visualizing whether the features in the dataset exhibit correlation among themselves or with the target variable that tells whether the pair matched or not. This is important as it will help us come up with blatant patterns observed in features that help in formulations of simple if-then rules. 
For the purposes of this visualization, we have narrowed down comparison of ratings to a specific question that were asked prior to the event - Distribute a score of 100 among the five attributes in the order of importance that you would like to see in your potential date.
  
This question is interesting to inspect if the attributes of what people look for in their potential partners bear any correlation among themselves and also with the actual number of people they agreed to match with.

```{r fig.width=15, fig.height=15}
columns = c("iid", "age", "race", "attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1")

df_distinct = df %>% group_by(iid, age, race, attr1_1, sinc1_1, intel1_1, fun1_1, amb1_1) %>% summarise(total_matches=sum(match))

ggpairs(df_distinct[c(columns,  "total_matches")], lower=list(combo=wrap("facethist")))+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),) +
  ggtitle("Pair plot for attributes and total number of people agreed to match")
```

Some of the interesting inferences we can make regarding the plots are,

* The distribution of most of the attributes are close to normal except for ambition with seems to be right skewed. A relatively high number of participants have given a low priority to ambition of their potential partners as a deciding factor.
* While most of the features are weakly negatively correlated almost exhibiting no correlation at all, the pair of feature sincerity, attractiveness and sincerity, intelligence are negatively correlated by the greatest amount. This tells us that people who gave a high preference to sincerity gave a low preference to intelligence and attractiveness and the other set of people weighed attractiveness and intelligence over sincerity.
* The age of the participants are mostly between 20 and 30, while one senior participant over 50 did not match with anyone, evident by the anomaly of the farthest point in the age vs total_matches plot.
* The trend that is seen in all the plots of attributes of attractiveness, sincerity, intelligence, fun and ambition is that, as the rating or the priority of certain feature increases, the number of matches goes down, for a few points. This is justifiable with the points that are to the farthest right at the bottom. This is expected as participants who have a really high expectation on one feature might not find someone suitable to meet their high expectations on that feature.
* It is interesting to note that the same plot of features vs total matches also exhibits some anomaly. There seems to be one point in all these plots that have a relatively medium level rating/priority while the number of matches is pretty high. This can be verified by the top most point to the left of the plots. There were some participants who are estimated to have based their criteria of matching on factors others that the ones that were rated on. This can be infered as they have a relatively high number of matches than their peers who matched less, given the same priority for those features.

## Analysis of decision making on categorical variable - Race

One of the factors of taken into consideration for understanding the requirements of participant's expectation with their partners is the Race. Each participant is required to report a rating out of 10 for their potential partner to be of the same race as them. This visualization is to analyze whether the actual decision of the partcipants is influenced by any other factors that overpowers them to match with their dates from Race other than their own. 

The following hexmap is a visual of Proportion of Matches that interested the participants from the same Race vs Importance of Race reported before the actual experiment. 

```{r}

filtered_df = df %>% filter(wave %in% (10:21))
filtered_df['samerace'] = (filtered_df$race==filtered_df$race_o)
matched_df = filtered_df %>% 
  filter(match==1) %>% 
  group_by(iid, samerace, imprace) %>% 
  summarise(race_match=sum(match)) %>% 
  filter(samerace==1)

total_match = df %>% group_by(iid) %>% summarise(total_matches=sum(match))
final_df_count = merge(matched_df, total_match, by='iid', all.x = TRUE)
final_df_count['race_match_proportion'] = final_df_count['race_match'] / final_df_count['total_matches']
# take scatter plot of race_match_proportion and imprace
ggplot(final_df_count, aes(imprace, race_match_proportion)) +
  geom_hex(bins=8) +
  scale_fill_gradient(low='#B3ECAD', high='darkslategrey') +
  theme(panel.border = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) 

```

The hexmap uncovers some interesting patterns observed from the participants' responses,

* There are instances of participants matching with only participants of different Races irrespective of their response to Importance of same Race. This indicates that Race is clearly not the sole factor for making a decision of matching with people.
* There is one anomaly at the top right hex cell which has the highest count of people matching with participants of the same Race despite giving a lower priority on importance of same Race.
* The count of people who have a high importance to matching with the same Race but indeed have agreed to match with the same Race are relatively low. This is indicated by light green hex patches implying a lower frequency of people matching within their own race.
* The presence of hexagons on the lower proportion of matches within the same race for higher values of importance of Race is intriguing. From this we can infer that participants who were strongly inclined to match with their own Race, changed their mind after the experiment. This gives a clear indicator that other attributes of a person overpowered their mindset of same Race.

## Attribute Rating Analysis by Race  

From the previous plot we inferred that certain attributes are strong enough to change participant's prior perception of importance of Race. Diving further, we want to understand how the attributes are rated for differently across the Race of the participants. This sheds light on how certain group of participants, characteristically from a certain Race, have prioritized attributes in their potential partners. 
Below is a mosaic plot for two specific features - attractiveness and ambition as independent features and visualized by Race as the dependent variable.

```{r fig.width=15, fig.height=15}

df_distinct$amb1_1 = round(df_distinct$amb1_1+5, -1)
df_distinct$attr1_1 = round(df_distinct$attr1_1+5, -1)

amb = grid.grabExpr(mosaic(race ~ amb1_1, direction = c("v", "h"), df_distinct, highlighting_fill = c('darkolivegreen4', 'darkolivegreen2', 'darkseagreen3', 'darkslategrey', 'chartreuse3')))
attr = grid.grabExpr(mosaic(race ~ attr1_1, direction = c("v", "h"), df_distinct, highlighting_fill = c('darkolivegreen4', 'darkolivegreen2', 'darkseagreen3', 'darkslategrey', 'chartreuse3')))
grid.arrange(amb, attr, nrow=1)

```

Some of the inferences we can draw from the above mosaic plots of attributes - attractiveness and ambition are,
  
* Race 2 - Majority of the participants are from Race 2 and the distribution of importance for ambition is split from 0 to 20. The same 

## Change of feature perception with time

Here, our objective is to find that if a participant's perspective (ratings) on which features they are looking for in the opposite sex change with time, especially before and after the speed dating experiment. For this part, we chose one question in particular from the survey: 

**What you look for in the opposite sex?**

Now, this question was asked to the same people multiple times. We specifically choose three times. The times we chose were: 

1) Asked before the speed dating experiment

2) Asked the day after the speed dating experiment

3) Asked 3-4 weeks after the speed dating experiment

To answer our question, we decided to use parallel coordinate axis plots since it helps us to visualize multiple variables at once and also account for correlations among the variables by comparing the direction of the lines (which are our participants in this case). We color coded them by gender to find more inferences. Again, we used waves 10-21 for this plot.

We did this for each of the five features: Attractiveness, Sincerity, Intelligence, Fun, and Ambition. We normalized the values of each variable in the plots using the `uniminmax` scale. We did not use splines because we believe we lost information if we include it.

Here are the plots:

```{r fig.width=10, fig.height=10}
col_common = c("iid", "pid", "gender", "match", "age", "field", "race", "from", "income", "goal", "career", "wave")
df_a = df[c(col_common, "attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1",
                            "attr1_2", "sinc1_2", "intel1_2", "fun1_2", "amb1_2",
                            "attr1_3", "sinc1_3", "intel1_3", "fun1_3", "amb1_3")]

df_a <- df_a[which(df_a$wave >= 10),]
df_a$iid = as.factor(df_a$iid)

df_1_a = df_a %>% 
  select(iid, attr1_1, attr1_2, attr1_3, match, gender)

df_1_a$gender = factor(df_1_a$gender, levels = c(0,1), labels = c("female","male"))
df_1_a = unique(df_1_a)

g_1_a = ggparcoord(df_1_a, columns = c(2:4), scale = "uniminmax", alphaLines = 0.75, groupColumn = "gender") +
  scale_colour_manual(values = c("#77D86C", "#DD8C75")) +
  xlab("Variables") +
  ylab("Normalized ratings/match values") +
  ggtitle("Perception of Attractiveness with time")




df_1_b = df_a %>% 
  select(iid, sinc1_1, sinc1_2, sinc1_3, match, gender)

df_1_b$gender = factor(df_1_b$gender, levels = c(0,1), labels = c("female","male"))
df_1_b = unique(df_1_b)

g_1_b = ggparcoord(df_1_b, columns = c(2:4), scale = "uniminmax", alphaLines = 0.75, groupColumn = "gender") +
  scale_colour_manual(values = c("#77D86C", "#DD8C75")) +
  xlab("Variables") +
  ylab("Normalized ratings/match values") +
  ggtitle("Perception of Sincerity with time")



df_1_c = df_a %>% 
  select(iid, intel1_1, intel1_2, intel1_3, match, gender)

df_1_c$gender = factor(df_1_c$gender, levels = c(0,1), labels = c("female","male"))
df_1_c = unique(df_1_c)

g_1_c = ggparcoord(df_1_c, columns = c(2:4), scale = "uniminmax", alphaLines = 0.75, groupColumn = "gender") +
  scale_colour_manual(values = c("#77D86C", "#DD8C75")) +
  xlab("Variables") +
  ylab("Normalized ratings/match values") +
  ggtitle("Perception of Intelligence with time")



df_1_d = df_a %>% 
  select(iid, fun1_1, fun1_2, fun1_3, match, gender)

df_1_d$gender = factor(df_1_d$gender, levels = c(0,1), labels = c("female","male"))
df_1_d = unique(df_1_d)

g_1_d = ggparcoord(df_1_d, columns = c(2:4), scale = "uniminmax", alphaLines = 0.75, groupColumn = "gender") +
  scale_colour_manual(values = c("#77D86C", "#DD8C75")) +
  xlab("Variables") +
  ylab("Normalized ratings/match values") +
  ggtitle("Perception of Fun with time")



df_1_e = df_a %>% 
  select(iid, amb1_1, amb1_2, amb1_3, match, gender)

df_1_e$gender = factor(df_1_e$gender, levels = c(0,1), labels = c("female","male"))
df_1_e = unique(df_1_e)

g_1_e = ggparcoord(df_1_e, columns = c(2:4), scale = "uniminmax", alphaLines = 0.75, groupColumn = "gender") +
  scale_colour_manual(values = c("#77D86C", "#DD8C75")) +
  xlab("Variables") +
  ylab("Normalized ratings/match values") +
  ggtitle("Perception of Ambition with time")

g_1_123 = (g_1_a + g_1_b)/(g_1_c + g_1_d)/g_1_e
g_1_123
```

Here are the interpretations from the above plot:

**1) For Attractiveness**

Since most lines go slightly upwards from `attr1_1` to `attr1_2`, we can say that people give slightly more importance to the attractiveness of the other person a day after the speed dating experiment. From `attr1_2` to `attr1_3`, most lines go upward but some go downward. Hence, in general, most people give significant importance to the attractiveness of the partner. We can observe that few people drastically bring their rating from 25% to 100%, while some people reach 0% rating in 3-4 weeks. In general, the importance of attractiveness usually keeps increasing for males more, while there is no pattern for females. However, the increase of importance for females is more drastic in females.

**2) For Sincerity**

Since most lines go upwards from `sinc1_1` to `sinc1_2`, we can say that people give more importance to the sincerity of the other person the next day. From `sinc1_2` to `sinc1_3`, most lines go downward indicating that as most time passes (line 3-4 weeks), most people give less importance to the sincerity of the partner. For females, the importance of sincerity increases the day after the experiment, but reduces drastically in 3-4 weeks. For males, their sincerity importance level remained steady with time.

**3) For Intelligence**

Most lines go upwards from `intel1_1` to `intel1_2`, some go downward, and some remain steady (especially the one with zero rating). Generally speaking, we can say that people give more intelligence to the sincerity right after the speed dating experiment. From `intel1_2` to `intel1_3`, most lines remain steady, many go downward, and some go upward indicating that as most people remain around at similar levels or remain indifferent of their partner's intelligence. For most males, the importance of intelligence increased after the experiment and remained steady afterward. For most females, it first increased too and then decreased.

**4) For Fun**

There does not seem to be a pattern from `fun1_1` to `fun1_2` or from `fun1_2` to `fun1_3` since many lines go upward and downward both times. Moreover, the variation in the range of ratings keep increasing from `fun1_1` to `fun1_3`. Here too, the ratings of people with zero rating remained steady. No pattern is observed for particular genders.

**5) For Ambition**

Since most lines go upwards from `amb1_1` to `amb1_2`, we can say that people give more importance to the ambition of the other person the next day. From `amb1_2` to `amb1_3`, most lines go downward indicating that as most time passes (line 3-4 weeks), most people give less importance to the ambition of the partner. Here too, the ratings of people with zero rating remained steady. Moreover, some drastic increase (about 60% to 100%) and decrease (60% to 0%) of the importance of ambition is observed from `amb1_1` to `amb1_3`. For females, the importance of ambition increased after the experiment, but decreased again in 3-4 weeks. For males, there seems to be an even distribution of people with increasing and decreasing importance.

```{r}
# Explanation and headings to be filled for these sections
```

## Subsetting Dataset 

```{r}
df_work <- df[c(col_common, "attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1",
                            "attr2_1", "sinc2_1", "intel2_1", "fun2_1", "amb2_1",
                            "attr4_1", "sinc4_1", "intel4_1", "fun4_1", "amb4_1",
                            "attr1_2", "sinc1_2", "intel1_2", "fun1_2", "amb1_2",
                            "attr2_2", "sinc2_2", "intel2_2", "fun2_2", "amb2_2",
                            "attr4_2", "sinc4_2", "intel4_2", "fun4_2", "amb4_2",
                            "satis_2")]
df_work <- df_work[ which(df_work$wave >= 10),]
```

```{r}
df_pre <- df_work[c(col_common, "attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1",
                            "attr2_1", "sinc2_1", "intel2_1", "fun2_1", "amb2_1",
                            "attr4_1", "sinc4_1", "intel4_1", "fun4_1", "amb4_1")]
df_pre <- df_pre[ which(df_pre$wave >= 10),]


```


```{r}
df_post <- df_work[c(col_common, "attr1_2", "sinc1_2", "intel1_2", "fun1_2", "amb1_2",
                            "attr2_2", "sinc2_2", "intel2_2", "fun2_2", "amb2_2",
                            "attr4_2", "sinc4_2", "intel4_2", "fun4_2", "amb4_2",
                            "satis_2")]
df_post <- df_post[ which(df_post$wave >= 10),]


```

```{r}
df_bar_f_pre <- df_pre[c("iid","gender","attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1")]
df_bar_f_pre<- df_bar_f_pre[ which(df_bar_f_pre$gender == 0),]

df_bar_f_pre<- df_bar_f_pre %>%
                      	group_by(iid,gender) %>%
                      	summarise(mean_attr1_1 = mean(attr1_1),
                      	          mean_sinc1_1 = mean(sinc1_1),
                      	          mean_intel1_1 = mean(intel1_1),
                      	          mean_fun1_1 = mean(fun1_1),
                      	          mean_amb1_1 = mean(amb1_1))

df_bar_f_pre <- pivot_longer(data = df_bar_f_pre, cols = c("mean_attr1_1", "mean_sinc1_1", "mean_intel1_1", "mean_fun1_1", "mean_amb1_1"))
df_bar_f_pre$value[is.na(df_bar_f_pre$value)]<-mean(df_bar_f_pre$value,na.rm=TRUE)



```

```{r}
df_bar_f_post <- df_post[c("iid","gender","attr1_2", "sinc1_2", "intel1_2", "fun1_2", "amb1_2")]
df_bar_f_post <- df_bar_f_post[ which(df_bar_f_post$gender == 0),]
df_bar_f_post <- df_bar_f_post %>%
                      	group_by(iid,gender) %>%
                      	summarise(mean_attr1_2 = mean(attr1_2),
                      	          mean_sinc1_2 = mean(sinc1_2),
                      	          mean_intel1_2 = mean(intel1_2),
                      	          mean_fun1_2 = mean(fun1_2),
                      	          mean_amb1_2 = mean(amb1_2))

df_bar_f_post <- pivot_longer(data = df_bar_f_post, cols = c("mean_attr1_2", "mean_sinc1_2", "mean_intel1_2", "mean_fun1_2", "mean_amb1_2"))
df_bar_f_post$value[is.na(df_bar_f_post$value)]<-mean(df_bar_f_post$value,na.rm=TRUE)
```

```{r}
df_bar_m_pre <- df_pre[c("iid","gender","attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1")]
df_bar_m_pre<- df_bar_m_pre[ which(df_bar_m_pre$gender == 1),]
df_bar_m_pre<- df_bar_m_pre %>%
                      	group_by(iid,gender) %>%
                      	summarise(mean_attr1_1 = mean(attr1_1),
                      	          mean_sinc1_1 = mean(sinc1_1),
                      	          mean_intel1_1 = mean(intel1_1),
                      	          mean_fun1_1 = mean(fun1_1),
                      	          mean_amb1_1 = mean(amb1_1))
# d1 <- pivot_longer(!iid, names_to = "colmn_names", values_to = "colmn_val")
df_bar_m_pre <- pivot_longer(data = df_bar_m_pre, cols = c("mean_attr1_1", "mean_sinc1_1", "mean_intel1_1", "mean_fun1_1", "mean_amb1_1"))
df_bar_m_pre$value[is.na(df_bar_m_pre$value)]<-mean(df_bar_m_pre$value,na.rm=TRUE)
```

```{r}
df_bar_m_post <- df_post[c("iid","gender","attr1_2", "sinc1_2", "intel1_2", "fun1_2", "amb1_2")]
df_bar_m_post <- df_bar_m_post[ which(df_bar_m_post$gender == 1),]
df_bar_m_post <- df_bar_m_post %>%
                      	group_by(iid,gender) %>%
                      	summarise(mean_attr1_2 = mean(attr1_2),
                      	          mean_sinc1_2 = mean(sinc1_2),
                      	          mean_intel1_2 = mean(intel1_2),
                      	          mean_fun1_2 = mean(fun1_2),
                      	          mean_amb1_2 = mean(amb1_2))
# d1 <- pivot_longer(!iid, names_to = "colmn_names", values_to = "colmn_val")
df_bar_m_post <- pivot_longer(data = df_bar_m_post, cols = c("mean_attr1_2", "mean_sinc1_2", "mean_intel1_2", "mean_fun1_2", "mean_amb1_2"))
df_bar_m_post$value[is.na(df_bar_m_post$value)]<-mean(df_bar_m_post$value,na.rm=TRUE)
```

```{r}
# bar plots for gender female pre
p1 <- df_bar_f_pre %>% ggplot(mapping = aes(x=reorder(name, -value), y=value, fill = name)) +
  geom_bar(stat = 'summary', fun = 'mean', color = "#000000") +
  scale_x_discrete("Attributes", labels = c("mean_attr1_1" = "Attractive", "mean_sinc1_1" = "Sincerity", "mean_intel1_1" = 
                                              "Intelligence", "mean_fun1_1" = "Fun", "mean_amb1_1" = "Ambition")) + 
  scale_fill_brewer(palette = "Pastel1", name = "Attributes", labels = c("ambition", "attractiveness", 
                                                                        "fun","intelligence","sincerity")) +
  theme_gray(10) +
  ylab("Ratings out of 100") + 
  xlab("Atrributes") + 
  ggtitle("Female - Before Experiment")

# bar plots for gender Female post
p2 <- df_bar_f_post %>% ggplot(mapping = aes(x=reorder(name, -value), y=value, fill = name)) +
  geom_bar(stat = 'summary', fun = 'mean', color = "#000000") +
  scale_x_discrete("Attributes", labels = c("mean_attr1_2" = "Attractive", "mean_sinc1_2" = "Sincerity", "mean_intel1_2" = 
                                              "Intelligence", "mean_fun1_2" = "Fun", "mean_amb1_2" = "Ambition")) + 
  scale_fill_brewer(palette = "Pastel1", name = "Attributes", labels = c("ambition", "attractiveness", 
                                                                        "fun","intelligence","sincerity")) +
  theme_gray(10) + 
  ylab("Ratings out of 100") + 
  xlab("Atrributes") + 
  ggtitle("Female - After Experiment")

p3 <- ggarrange(p1, p2, ncol=2, common.legend = TRUE, legend="bottom")

annotate_figure(p3, top = textGrob("Importance of different Attributes for each Gender Group",gp=gpar(fontsize=15)))

# bar plots for gender Male pre
p4<- df_bar_m_pre %>% ggplot(mapping = aes(x=reorder(name, -value), y=value, fill = name)) +
  geom_bar(stat = 'summary', fun = 'mean', color = "#000000") +
  scale_x_discrete("Attributes", labels = c("mean_attr1_1" = "Attractive", "mean_sinc1_1" = "Sincerity", "mean_intel1_1" = 
                                              "Intelligence", "mean_fun1_1" = "Fun", "mean_amb1_1" = "Ambition")) + 
  scale_fill_brewer(palette = "Pastel1", name = "Attributes", labels = c("ambition", "attractiveness", 
                                                                        "fun","intelligence","sincerity")) +
  theme_gray(10) +
  ylab("Ratings out of 100") + 
  xlab("Atrributes") + 
  ggtitle("Male - Before Experiment")

# bar plots for gender Male post
p5 <- df_bar_m_post %>% ggplot(mapping = aes(x=reorder(name, -value), y=value, fill = name)) +
  geom_bar(stat = 'summary', fun = 'mean', color = "#000000") +
  scale_x_discrete("Attributes", labels = c("mean_attr1_2" = "Attractive", "mean_sinc1_2" = "Sincerity", "mean_intel1_2" = 
                                              "Intelligence", "mean_fun1_2" = "Fun", "mean_amb1_2" = "Ambition")) + 
  scale_fill_brewer(palette = "Pastel1", name = "Attributes", labels = c("ambition", "attractiveness", 
                                                                        "fun","intelligence","sincerity")) +
  theme_gray(10) +
  ylab("Ratings out of 100") + 
  xlab("Atrributes") + 
  ggtitle("Male - After Experiment")

p6 <- ggarrange(p4, p5, ncol=2, common.legend = TRUE, legend="bottom")

annotate_figure(p6, top = textGrob("Importance of different Attributes for each Gender Group",gp=gpar(fontsize=15)))

```
Before the Speed Dating experiment all the participants were asked to rate how important are these five attributes – Ambition, Attractiveness, Fun, Intelligence, Sincerity. They were asked to distribute 100 points across these attributes.

It can be observed from the 1st plot that that most women before the Speed Dating Experiment rated Intelligence as most important attribute followed by Sincerity then Attractiveness. Whereas after the experiment women rated Attractiveness as the most important attribute followed by Intelligence then Sincerity.

It can be observed from the 2nd plot that most men before the Speed Dating Experiment rated Attractiveness as most important attribute followed by Intelligence then Fun. Even after the Experiment men rated Attractiveness as the most important attribute followed by Fun then Intelligence.

For both gender groups it can be observed that Ambition has been rated as the least important attribute. To female, the top three attributes are Intelligence, Sincerity and Attractiveness, while to male, they were Attractiveness, Intelligence and Fun. Also, it can be observed that men tended to have more distinctive preference whereas women’s preference appeared to be more even.

```{r}
df_bar_pre <- df_pre[c("gender","attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1",
                                          "attr2_1", "sinc2_1", "intel2_1", "fun2_1", "amb2_1",
                                          "attr4_1", "sinc4_1", "intel4_1", "fun4_1", "amb4_1")]
for(i in 1:ncol(df_bar_pre)){
  df_bar_pre[is.na(df_bar_pre[,i]), i] <- mean(df_bar_pre[,i], na.rm = TRUE)
}
df_bar_pre <- df_bar_pre %>% 
                    group_by(gender) %>%
                      summarise(across(everything(), mean))
```


```{r}
df_bar_pre_f <- df_bar_pre[ which(df_bar_pre$gender == 0),]
df_bar_pre_f <- select(df_bar_pre_f,-c("gender","attr4_1", "sinc4_1", "intel4_1", "fun4_1", "amb4_1"))
df_bar_pre_f_1 <- df_bar_pre[ which(df_bar_pre$gender == 1),]
df_bar_pre_f_1 <- select(df_bar_pre_f_1,-c("gender","attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1",
                                                    "attr2_1", "sinc2_1", "intel2_1", "fun2_1", "amb2_1"))
df_bar_pre_f <- cbind(df_bar_pre_f, attr4_1 = df_bar_pre_f_1$attr4_1 , 
                                    sinc4_1 = df_bar_pre_f_1$sinc4_1 , 
                                    intel4_1 = df_bar_pre_f_1$intel4_1, 
                                    fun4_1 = df_bar_pre_f_1$fun4_1, 
                                    amb4_1 = df_bar_pre_f_1$amb4_1)
df_bar_pre_f <- pivot_longer(data = df_bar_pre_f, 
                             cols = c("attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1",
                                          "attr2_1", "sinc2_1", "intel2_1", "fun2_1", "amb2_1",
                                          "attr4_1", "sinc4_1", "intel4_1", "fun4_1", "amb4_1"))
df_bar_pre_f$Attribute <- substr(df_bar_pre_f$name, 0, 3)
df_bar_pre_plt_f <- df_bar_pre_f%>% 
  gather(Attr, plot_v, -c(Attribute, value)) %>%
    mutate(Attribute = factor(Attribute, 
                        levels = c("att", "sin", "int", "fun", "amb"))) %>%
      arrange(Attribute)
```

```{r}
df_bar_pre_m <- df_bar_pre[ which(df_bar_pre$gender == 1),]
df_bar_pre_m <- select(df_bar_pre_m,-c("gender","attr4_1", "sinc4_1", "intel4_1", "fun4_1", "amb4_1"))
df_bar_pre_m_1 <- df_bar_pre[ which(df_bar_pre$gender == 0),]
df_bar_pre_m_1 <- select(df_bar_pre_m_1,-c("gender","attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1",
                                                    "attr2_1", "sinc2_1", "intel2_1", "fun2_1", "amb2_1"))
df_bar_pre_m <- cbind(df_bar_pre_m, attr4_1 = df_bar_pre_m_1$attr4_1 , 
                                    sinc4_1 = df_bar_pre_m_1$sinc4_1 , 
                                    intel4_1 = df_bar_pre_m_1$intel4_1, 
                                    fun4_1 = df_bar_pre_m_1$fun4_1, 
                                    amb4_1 = df_bar_pre_m_1$amb4_1)
df_bar_pre_m <- pivot_longer(data = df_bar_pre_m, 
                             cols = c("attr1_1", "sinc1_1", "intel1_1", "fun1_1", "amb1_1",
                                          "attr2_1", "sinc2_1", "intel2_1", "fun2_1", "amb2_1",
                                          "attr4_1", "sinc4_1", "intel4_1", "fun4_1", "amb4_1"))
df_bar_pre_m$Attribute <- substr(df_bar_pre_m$name, 0, 3)
df_bar_pre_plt_m <- df_bar_pre_m%>% 
  gather(Attr, plot_v, -c(Attribute, value)) %>%
    mutate(Attribute = factor(Attribute, 
                        levels = c("att", "sin", "int", "fun", "amb"))) %>%
      arrange(Attribute)

```


```{r}
df_bar_post <- df_post[c("gender","attr1_2", "sinc1_2", "intel1_2", "fun1_2", "amb1_2",
                                          "attr2_2", "sinc2_2", "intel2_2", "fun2_2", "amb2_2",
                                          "attr4_2", "sinc4_2", "intel4_2", "fun4_2", "amb4_2")]
for(i in 1:ncol(df_bar_post)){
  df_bar_post[is.na(df_bar_post[,i]), i] <- mean(df_bar_post[,i], na.rm = TRUE)
}
df_bar_post <- df_bar_post %>% 
                    group_by(gender) %>%
                      summarise(across(everything(), mean))
```


```{r}
df_bar_post_f <- df_bar_post[ which(df_bar_pre$gender == 0),]
df_bar_post_f <- select(df_bar_post_f,-c("gender","attr4_2", "sinc4_2", "intel4_2", "fun4_2", "amb4_2"))
df_bar_post_f_1 <- df_bar_post[ which(df_bar_post$gender == 1),]
df_bar_post_f_1 <- select(df_bar_post_f_1,-c("gender","attr1_2", "sinc1_2", "intel1_2", "fun1_2", "amb1_2",
                                                    "attr2_2", "sinc2_2", "intel2_2", "fun2_2", "amb2_2"))
df_bar_post_f <- cbind(df_bar_post_f, attr4_2 = df_bar_post_f_1$attr4_2 , 
                                    sinc4_2 = df_bar_post_f_1$sinc4_2 , 
                                    intel4_2 = df_bar_post_f_1$intel4_2, 
                                    fun4_2 = df_bar_post_f_1$fun4_2, 
                                    amb4_2 = df_bar_post_f_1$amb4_2)
df_bar_post_f <- pivot_longer(data = df_bar_post_f, 
                             cols = c("attr1_2", "sinc1_2", "intel1_2", "fun1_2", "amb1_2",
                                          "attr2_2", "sinc2_2", "intel2_2", "fun2_2", "amb2_2",
                                          "attr4_2", "sinc4_2", "intel4_2", "fun4_2", "amb4_2"))
df_bar_post_f$Attribute <- substr(df_bar_post_f$name, 0, 3)
df_bar_post_plt_f <- df_bar_post_f%>% 
  gather(Attr, plot_v, -c(Attribute, value)) %>%
    mutate(Attribute = factor(Attribute, 
                        levels = c("att", "sin", "int", "fun", "amb"))) %>%
      arrange(Attribute)
```

```{r}
df_bar_post_m <- df_bar_post[ which(df_bar_pre$gender == 1),]
df_bar_post_m <- select(df_bar_post_m,-c("gender","attr4_2", "sinc4_2", "intel4_2", "fun4_2", "amb4_2"))
df_bar_post_m_1 <- df_bar_post[ which(df_bar_pre$gender == 0),]
df_bar_post_m_1 <- select(df_bar_post_m_1,-c("gender","attr1_2", "sinc1_2", "intel1_2", "fun1_2", "amb1_2",
                                                    "attr2_2", "sinc2_2", "intel2_2", "fun2_2", "amb2_2"))
df_bar_post_m <- cbind(df_bar_post_m, attr4_2 = df_bar_post_m_1$attr4_2 , 
                                    sinc4_2 = df_bar_post_m_1$sinc4_2 , 
                                    intel4_2 = df_bar_post_m_1$intel4_2, 
                                    fun4_2 = df_bar_post_m_1$fun4_2, 
                                    amb4_2 = df_bar_post_m_1$amb4_2)
df_bar_post_m <- pivot_longer(data = df_bar_post_m, 
                             cols = c("attr1_2", "sinc1_2", "intel1_2", "fun1_2", "amb1_2",
                                          "attr2_2", "sinc2_2", "intel2_2", "fun2_2", "amb2_2",
                                          "attr4_2", "sinc4_2", "intel4_2", "fun4_2", "amb4_2"))
df_bar_post_m$Attribute <- substr(df_bar_post_m$name, 0, 3)
df_bar_post_plt_m <- df_bar_post_m%>% 
  gather(Attr, plot_v, -c(Attribute, value)) %>%
    mutate(Attribute = factor(Attribute, 
                        levels = c("att", "sin", "int", "fun", "amb"))) %>%
      arrange(Attribute)
```


```{r}
df_bar_pre_plt_f$plot_v[df_bar_pre_plt_f$plot_v=="attr1_1" | 
                         df_bar_pre_plt_f$plot_v=="sinc1_1" |
                         df_bar_pre_plt_f$plot_v=="intel1_1" |
                         df_bar_pre_plt_f$plot_v=="fun1_1" |
                         df_bar_pre_plt_f$plot_v=="amb1_1" ]<- "1_1" 

df_bar_pre_plt_f$plot_v[df_bar_pre_plt_f$plot_v=="attr2_1" | 
                         df_bar_pre_plt_f$plot_v=="sinc2_1" |
                         df_bar_pre_plt_f$plot_v=="intel2_1" |
                         df_bar_pre_plt_f$plot_v=="fun2_1" |
                         df_bar_pre_plt_f$plot_v=="amb2_1" ]<- "2_1" 

df_bar_pre_plt_f$plot_v[df_bar_pre_plt_f$plot_v=="attr4_1" | 
                         df_bar_pre_plt_f$plot_v=="sinc4_1" |
                         df_bar_pre_plt_f$plot_v=="intel4_1" |
                         df_bar_pre_plt_f$plot_v=="fun4_1" |
                         df_bar_pre_plt_f$plot_v=="amb4_1" ]<- "4_1" 

#--------------------------------------------------------------------------#

df_bar_pre_plt_m$plot_v[df_bar_pre_plt_m$plot_v=="attr1_1" | 
                         df_bar_pre_plt_m$plot_v=="sinc1_1" |
                         df_bar_pre_plt_m$plot_v=="intel1_1" |
                         df_bar_pre_plt_m$plot_v=="fun1_1" |
                         df_bar_pre_plt_m$plot_v=="amb1_1" ]<- "1_1" 

df_bar_pre_plt_m$plot_v[df_bar_pre_plt_m$plot_v=="attr2_1" | 
                         df_bar_pre_plt_m$plot_v=="sinc2_1" |
                         df_bar_pre_plt_m$plot_v=="intel2_1" |
                         df_bar_pre_plt_m$plot_v=="fun2_1" |
                         df_bar_pre_plt_m$plot_v=="amb2_1" ]<- "2_1" 

df_bar_pre_plt_m$plot_v[df_bar_pre_plt_m$plot_v=="attr4_1" | 
                         df_bar_pre_plt_m$plot_v=="sinc4_1" |
                         df_bar_pre_plt_m$plot_v=="intel4_1" |
                         df_bar_pre_plt_m$plot_v=="fun4_1" |
                         df_bar_pre_plt_m$plot_v=="amb4_1" ]<- "4_1" 

#--------------------------------------------------------------------------#

df_bar_post_plt_f$plot_v[df_bar_post_plt_f$plot_v=="attr1_2" | 
                         df_bar_post_plt_f$plot_v=="sinc1_2" |
                         df_bar_post_plt_f$plot_v=="intel1_2" |
                         df_bar_post_plt_f$plot_v=="fun1_2" |
                         df_bar_post_plt_f$plot_v=="amb1_2" ]<- "1_2" 

df_bar_post_plt_f$plot_v[df_bar_post_plt_f$plot_v=="attr2_2" | 
                         df_bar_post_plt_f$plot_v=="sinc2_2" |
                         df_bar_post_plt_f$plot_v=="intel2_2" |
                         df_bar_post_plt_f$plot_v=="fun2_2" |
                         df_bar_post_plt_f$plot_v=="amb2_2" ]<- "2_2" 

df_bar_post_plt_f$plot_v[df_bar_post_plt_f$plot_v=="attr4_2" | 
                         df_bar_post_plt_f$plot_v=="sinc4_2" |
                         df_bar_post_plt_f$plot_v=="intel4_2" |
                         df_bar_post_plt_f$plot_v=="fun4_2" |
                         df_bar_post_plt_f$plot_v=="amb4_2" ]<- "4_2" 

#--------------------------------------------------------------------------#

df_bar_post_plt_m$plot_v[df_bar_post_plt_m$plot_v=="attr1_2" | 
                         df_bar_post_plt_m$plot_v=="sinc1_2" |
                         df_bar_post_plt_m$plot_v=="intel1_2" |
                         df_bar_post_plt_m$plot_v=="fun1_2" |
                         df_bar_post_plt_m$plot_v=="amb1_2" ]<- "1_2" 

df_bar_post_plt_m$plot_v[df_bar_post_plt_m$plot_v=="attr2_2" | 
                         df_bar_post_plt_m$plot_v=="sinc2_2" |
                         df_bar_post_plt_m$plot_v=="intel2_2" |
                         df_bar_post_plt_m$plot_v=="fun2_2" |
                         df_bar_post_plt_m$plot_v=="amb2_2" ]<- "2_2" 

df_bar_post_plt_m$plot_v[df_bar_post_plt_m$plot_v=="attr4_2" | 
                         df_bar_post_plt_m$plot_v=="sinc4_2" |
                         df_bar_post_plt_m$plot_v=="intel4_2" |
                         df_bar_post_plt_m$plot_v=="fun4_2" |
                         df_bar_post_plt_m$plot_v=="amb4_2" ]<- "4_2" 

```


```{r}

p1 <- ggplot(data = df_bar_pre_plt_f) +
  geom_bar(aes(x = Attribute, y = value, fill = plot_v), stat = "identity", position = position_dodge(), color = "#000000") +
  scale_x_discrete("Attributes", labels = c("att" = "Attractive", "sin" = "Sincerity", "int" = "Intelligence", "fun" = "Fun", 
                                            "amb" = "Ambition")) + 
  scale_fill_brewer(palette = "Pastel1", name = "Questions", labels = c("female Rating", "opposite sex rating", 
                                                                        "fellow women rating")) +
  theme_gray(10) +
  theme(legend.title=element_blank()) + 
  ylab("Ratings out of 100") + 
  xlab("Atrributes") + 
  ggtitle("Female - Before Experiment")

p2 <- ggplot(data = df_bar_post_plt_f) +
  geom_bar(aes(x = Attribute, y = value, fill = plot_v), stat = "identity", position = position_dodge(), color = "#000000") +
  scale_x_discrete("Attributes", labels = c("att" = "Attractive", "sin" = "Sincerity", "int" = "Intelligence", "fun" = "Fun", 
                                            "amb" = "Ambition")) + 
  scale_fill_brewer(palette = "Pastel1", name = "Questions", labels = c("female Rating", "opposite sex rating", 
                                                                        "fellow women rating")) +
  theme_gray(10) +
  theme(legend.title=element_blank()) + 
  ylab("Ratings out of 100") + 
  xlab("Atrributes") + 
  ggtitle("Female - After Experiment")

p3 <- ggarrange(p1, p2, ncol=2, common.legend = TRUE, legend="bottom")

annotate_figure(p3, top = textGrob("Attribute Importance for Female",gp=gpar(fontsize=15)))

p4 <- ggplot(data = df_bar_pre_plt_m) +
  geom_bar(aes(x = Attribute, y = value, fill = plot_v), stat = "identity", position = position_dodge(), color = "#000000") +
  scale_x_discrete("Attributes", labels = c("att" = "Attractive", "sin" = "Sincerity", "int" = "Intelligence", "fun" = "Fun", 
                                            "amb" = "Ambition")) + 
  scale_fill_brewer(palette = "Pastel1", name = "Questions", labels = c("male Rating", "opposite sex rating", 
                                                                        "fellow men rating")) +
  theme_gray(10) +
  theme(legend.title=element_blank()) + 
  ylab("Ratings out of 100") + 
  xlab("Atrributes") + 
  ggtitle("Male - Before Experiment")

p5 <- ggplot(data = df_bar_post_plt_m) +
  geom_bar(aes(x = Attribute, y = value, fill = plot_v), stat = "identity", position = position_dodge(), color = "#000000") +
  scale_x_discrete("Attributes", labels = c("att" = "Attractive", "sin" = "Sincerity", "int" = "Intelligence", "fun" = "Fun", 
                                            "amb" = "Ambition")) + 
  scale_fill_brewer(palette = "Pastel1", name = "Questions", labels = c("male Rating", "opposite sex rating", 
                                                                        "fellow men rating")) +
  theme_gray(10) +
  theme(legend.title=element_blank()) + 
  ylab("Ratings out of 100") + 
  xlab("Atrributes") + 
  ggtitle("Male - After Experiment")

p6 <- ggarrange(p4, p5, ncol=2, common.legend = TRUE, legend="bottom")

annotate_figure(p6, top = textGrob("Attribute Importance for Male",gp=gpar(fontsize=15)))
```

Before the Speed Dating experiment all the participants were asked to rate how important are these five attributes – Ambition, Attractiveness, Fun, Intelligence, Sincerity. They were asked to distribute 100 points across these attributes. They were also asked to rate what they think opposite sex would rate and what fellow women/men would rate how important the attributes are.

We get this information from the questions 1_1, 2_1, 4_1 for the data before experiment and 1_2, 2_2, 4_2 for the data after experiment. We plotted the average rating given by individual vs the rating given by opposite sex vs the rating of what fellow women/men would rate the attributes.

It can be observed from the plot that most women do not consider Attractiveness to be an important attribute but think that fellow women consider Attractiveness to be an important attribute. Similarly, even men think that women consider Attractiveness to be most important attribute but in real life women consider Intelligence to be the most important attribute.

It can be observed from the plot that men consider Attractiveness to be the most important attribute and also perceive that the fellow men also have same perception that Attractiveness is the most important attribute. It can also be observed that the women’s perception of what men think the most important attribute is correct as most women gave high rating for what men might rate for each attribute.

Overall, it can be observed that women’s perception of what men consider about each attribute is very accurate whereas men’s perception of what women might consider as important attributes is inaccurate (It can be seen in the difference between the pink bar and blue bar).

```{r}
df_satis <- df_post[c("iid","gender","match", "satis_2")]
df_satis_f <- df_satis[ which(df_satis$gender == 0),]
df_satis_f_1 <- df_satis_f %>%
              group_by(iid) %>%
                summarise(no_matches = sum(match),
                          satisfied = median(satis_2))

df_satis_f_1 <- subset (df_satis_f_1 , select = -iid)
df_satis_f_1<-data.frame(table(df_satis_f_1))
df_satis_f_1$Freq<-as.factor(df_satis_f_1$Freq)
df_satis_f_1$no_matches<-as.character(df_satis_f_1$no_matches) %>% as.numeric()
df_satis_f_1$satisfied<-as.character(df_satis_f_1$satisfied) %>% as.numeric()

df_satis <- df_post[c("iid","gender","match", "satis_2")]
df_satis_m <- df_satis[ which(df_satis$gender == 1),]
df_satis_m_1 <- df_satis_m %>%
              group_by(iid) %>%
                summarise(no_matches = sum(match),
                          satisfied = median(satis_2))

df_satis_m_1 <- subset (df_satis_m_1 , select = -iid)
df_satis_m_1<-data.frame(table(df_satis_m_1))
df_satis_m_1$Freq<-as.factor(df_satis_m_1$Freq)
df_satis_m_1$no_matches<-as.character(df_satis_m_1$no_matches) %>% as.numeric()
df_satis_m_1$satisfied<-as.character(df_satis_m_1$satisfied) %>% as.numeric()

```

```{r}

# plot using ggplot
getPalette_10 = colorRampPalette(brewer.pal(9, "Greens"))

ggplot(df_satis_f_1,aes(x=no_matches,y=satisfied)) +
  geom_tile(aes(fill=Freq))+
  scale_fill_manual(values = (getPalette_10(25)[-1:-7]))+
  #theme_gray(10) +
  theme(legend.title=element_blank()) + 
  ylab("Satisfaction score out of 10") + 
  xlab("number of Matches") + 
  ggtitle("Satisfaction score vs no. of matches for Female")


ggplot(df_satis_m_1,aes(x=no_matches,y=satisfied)) +
  geom_tile(aes(fill=Freq)) +
  scale_fill_manual(values = (getPalette_10(25)[-1:-7]))+
  #theme_gray(10) +
  theme(legend.title=element_blank()) + 
  ylab("Satisfaction score out of 10") + 
  xlab("number of Matches") + 
  ggtitle("Satisfaction score vs no. of matches for Male")



```

## Subsetting Dataset 

```{r}
df_1 = df
df_1_work <- df_1[c(col_common, "attr3_1", "sinc3_1", "intel3_1", "fun3_1", "amb3_1",
                            "attr5_1", "sinc5_1", "intel5_1", "fun5_1", "amb5_1",
                            "attr3_2", "sinc3_2", "intel3_2", "fun3_2", "amb3_2",
                            "attr5_2", "sinc5_2", "intel5_2", "fun5_2", "amb5_2",
                            "attr_o", "sinc_o", "intel_o", "fun_o", "amb_o")]
df_1_work <- df_1_work[ which(df_1_work$wave >= 10),]
```

```{r}
df_1_pre <- df_1_work[c(col_common, "attr3_1", "sinc3_1", "intel3_1", "fun3_1", "amb3_1",
                            "attr5_1", "sinc5_1", "intel5_1", "fun5_1", "amb5_1",
                            "attr_o", "sinc_o", "intel_o", "fun_o", "amb_o")]
df_1_pre <- df_1_pre[ which(df_1_pre$wave >= 10),]
```


```{r}
df_1_post <- df_1_work[c(col_common, "attr3_2", "sinc3_2", "intel3_2", "fun3_2", "amb3_2",
                            "attr5_2", "sinc5_2", "intel5_2", "fun5_2", "amb5_2",
                            "attr_o", "sinc_o", "intel_o", "fun_o", "amb_o")]
df_1_post <- df_1_post[ which(df_1_post$wave >= 10),]
```

```{r}
df_box_pre <- df_1_pre[c("gender","attr3_1", "sinc3_1", "intel3_1", "fun3_1", "amb3_1",
                                          "attr5_1", "sinc5_1", "intel5_1", "fun5_1", "amb5_1",
                                          "attr_o", "sinc_o", "intel_o", "fun_o", "amb_o")]
for(i in 1:ncol(df_box_pre)){
  df_box_pre[is.na(df_box_pre[,i]), i] <- mean(df_box_pre[,i], na.rm = TRUE)
}
```


```{r}
df_box_pre_f <- df_box_pre[ which(df_box_pre$gender == 0),]
df_box_pre_f <- select(df_box_pre_f,-c("gender"))
df_box_pre_f <- pivot_longer(data = df_box_pre_f, 
                             cols = c("attr3_1", "sinc3_1", "intel3_1", "fun3_1", "amb3_1",
                                          "attr5_1", "sinc5_1", "intel5_1", "fun5_1", "amb5_1",
                                          "attr_o", "sinc_o", "intel_o", "fun_o", "amb_o"))
df_box_pre_f$Attribute <- substr(df_box_pre_f$name, 0, 3)
df_box_pre_plt_f <- df_box_pre_f%>% 
  gather(Attr, plot_v, -c(Attribute, value)) %>%
    mutate(Attribute = factor(Attribute, 
                        levels = c("att", "sin", "int", "fun", "amb"))) %>%
      arrange(Attribute)
```

```{r}
df_box_pre_m <- df_box_pre[ which(df_box_pre$gender == 1),]
df_box_pre_m <- select(df_box_pre_m,-c("gender"))
df_box_pre_m <- pivot_longer(data = df_box_pre_m, 
                             cols = c("attr3_1", "sinc3_1", "intel3_1", "fun3_1", "amb3_1",
                                          "attr5_1", "sinc5_1", "intel5_1", "fun5_1", "amb5_1",
                                          "attr_o", "sinc_o", "intel_o", "fun_o", "amb_o"))
df_box_pre_m$Attribute <- substr(df_box_pre_m$name, 0, 3)
df_box_pre_plt_m <- df_box_pre_m%>% 
  gather(Attr, plot_v, -c(Attribute, value)) %>%
    mutate(Attribute = factor(Attribute, 
                        levels = c("att", "sin", "int", "fun", "amb"))) %>%
      arrange(Attribute)
```


```{r}
df_box_post <- df_1_post[c("gender","attr3_2", "sinc3_2", "intel3_2", "fun3_2", "amb3_2",
                                          "attr5_2", "sinc5_2", "intel5_2", "fun5_2", "amb5_2",
                                          "attr_o", "sinc_o", "intel_o", "fun_o", "amb_o")]
for(i in 1:ncol(df_box_post)){
  df_box_post[is.na(df_box_post[,i]), i] <- mean(df_box_post[,i], na.rm = TRUE)
}
```


```{r}
df_box_post_f <- df_box_post[ which(df_box_pre$gender == 0),]
df_box_post_f <- select(df_box_post_f,-c("gender"))
df_box_post_f <- pivot_longer(data = df_box_post_f, 
                             cols = c("attr3_2", "sinc3_2", "intel3_2", "fun3_2", "amb3_2",
                                          "attr5_2", "sinc5_2", "intel5_2", "fun5_2", "amb5_2",
                                          "attr_o", "sinc_o", "intel_o", "fun_o", "amb_o"))
df_box_post_f$Attribute <- substr(df_box_post_f$name, 0, 3)
df_box_post_plt_f <- df_box_post_f%>% 
  gather(Attr, plot_v, -c(Attribute, value)) %>%
    mutate(Attribute = factor(Attribute, 
                        levels = c("att", "sin", "int", "fun", "amb"))) %>%
      arrange(Attribute)
```

```{r}
df_box_post_m <- df_box_post[ which(df_box_pre$gender == 1),]
df_box_post_m <- select(df_box_post_m,-c("gender"))
df_box_post_m <- pivot_longer(data = df_box_post_m, 
                             cols = c("attr3_2", "sinc3_2", "intel3_2", "fun3_2", "amb3_2",
                                          "attr5_2", "sinc5_2", "intel5_2", "fun5_2", "amb5_2",
                                          "attr_o", "sinc_o", "intel_o", "fun_o", "amb_o"))
df_box_post_m$Attribute <- substr(df_box_post_m$name, 0, 3)
df_box_post_plt_m <- df_box_post_m%>% 
  gather(Attr, plot_v, -c(Attribute, value)) %>%
    mutate(Attribute = factor(Attribute, 
                        levels = c("att", "sin", "int", "fun", "amb"))) %>%
      arrange(Attribute)
```


```{r}
df_box_pre_plt_f$plot_v[df_box_pre_plt_f$plot_v=="attr3_1" | 
                         df_box_pre_plt_f$plot_v=="sinc3_1" |
                         df_box_pre_plt_f$plot_v=="intel3_1" |
                         df_box_pre_plt_f$plot_v=="fun3_1" |
                         df_box_pre_plt_f$plot_v=="amb3_1" ]<- "3_1" 

df_box_pre_plt_f$plot_v[df_box_pre_plt_f$plot_v=="attr5_1" | 
                         df_box_pre_plt_f$plot_v=="sinc5_1" |
                         df_box_pre_plt_f$plot_v=="intel5_1" |
                         df_box_pre_plt_f$plot_v=="fun5_1" |
                         df_box_pre_plt_f$plot_v=="amb5_1" ]<- "5_1" 

df_box_pre_plt_f$plot_v[df_box_pre_plt_f$plot_v=="attr_o" | 
                         df_box_pre_plt_f$plot_v=="sinc_o" |
                         df_box_pre_plt_f$plot_v=="intel_o" |
                         df_box_pre_plt_f$plot_v=="fun_o" |
                         df_box_pre_plt_f$plot_v=="amb_o" ]<- "_o" 

#--------------------------------------------------------------------------#

df_box_pre_plt_m$plot_v[df_box_pre_plt_m$plot_v=="attr3_1" | 
                         df_box_pre_plt_m$plot_v=="sinc3_1" |
                         df_box_pre_plt_m$plot_v=="intel3_1" |
                         df_box_pre_plt_m$plot_v=="fun3_1" |
                         df_box_pre_plt_m$plot_v=="amb3_1" ]<- "3_1" 

df_box_pre_plt_m$plot_v[df_box_pre_plt_m$plot_v=="attr5_1" | 
                         df_box_pre_plt_m$plot_v=="sinc5_1" |
                         df_box_pre_plt_m$plot_v=="intel5_1" |
                         df_box_pre_plt_m$plot_v=="fun5_1" |
                         df_box_pre_plt_m$plot_v=="amb5_1" ]<- "5_1" 

df_box_pre_plt_m$plot_v[df_box_pre_plt_m$plot_v=="attr_o" | 
                         df_box_pre_plt_m$plot_v=="sinc_o" |
                         df_box_pre_plt_m$plot_v=="intel_o" |
                         df_box_pre_plt_m$plot_v=="fun_o" |
                         df_box_pre_plt_m$plot_v=="amb_o" ]<- "_o" 

#--------------------------------------------------------------------------#

df_box_post_plt_f$plot_v[df_box_post_plt_f$plot_v=="attr3_2" | 
                         df_box_post_plt_f$plot_v=="sinc3_2" |
                         df_box_post_plt_f$plot_v=="intel3_2" |
                         df_box_post_plt_f$plot_v=="fun3_2" |
                         df_box_post_plt_f$plot_v=="amb3_2" ]<- "3_2" 

df_box_post_plt_f$plot_v[df_box_post_plt_f$plot_v=="attr5_2" | 
                         df_box_post_plt_f$plot_v=="sinc5_2" |
                         df_box_post_plt_f$plot_v=="intel5_2" |
                         df_box_post_plt_f$plot_v=="fun5_2" |
                         df_box_post_plt_f$plot_v=="amb5_2" ]<- "5_2" 

df_box_post_plt_f$plot_v[df_box_post_plt_f$plot_v=="attr_o" | 
                         df_box_post_plt_f$plot_v=="sinc_o" |
                         df_box_post_plt_f$plot_v=="intel_o" |
                         df_box_post_plt_f$plot_v=="fun_o" |
                         df_box_post_plt_f$plot_v=="amb_o" ]<- "_o" 

#--------------------------------------------------------------------------#

df_box_post_plt_m$plot_v[df_box_post_plt_m$plot_v=="attr3_2" | 
                         df_box_post_plt_m$plot_v=="sinc3_2" |
                         df_box_post_plt_m$plot_v=="intel3_2" |
                         df_box_post_plt_m$plot_v=="fun3_2" |
                         df_box_post_plt_m$plot_v=="amb3_2" ]<- "3_2" 

df_box_post_plt_m$plot_v[df_box_post_plt_m$plot_v=="attr5_2" | 
                         df_box_post_plt_m$plot_v=="sinc5_2" |
                         df_box_post_plt_m$plot_v=="intel5_2" |
                         df_box_post_plt_m$plot_v=="fun5_2" |
                         df_box_post_plt_m$plot_v=="amb5_2" ]<- "5_2" 

df_box_post_plt_m$plot_v[df_box_post_plt_m$plot_v=="attr_o" | 
                         df_box_post_plt_m$plot_v=="sinc_o" |
                         df_box_post_plt_m$plot_v=="intel_o" |
                         df_box_post_plt_m$plot_v=="fun_o" |
                         df_box_post_plt_m$plot_v=="amb_o" ]<- "_o" 

```


```{r}

p1 <-  ggplot(data = df_box_pre_plt_f, aes(x = Attribute, y = value, fill = plot_v), color = "#000000") +
        geom_boxplot() +
        scale_x_discrete("Attributes", labels = c("att" = "Attractive", "sin" = "Sincerity", "int" = "Intelligence", "fun" = 
                                                    "Fun", "amb" = "Ambition")) +
        scale_fill_brewer(palette = "Pastel1", name = "Perception", labels = c("Actual Rating", "Self Perception", 
                                                                        "Assumed Perception")) +
        theme_gray(10) +
        theme(legend.title=element_blank()) + 
        ylab("Ratings out of 10") + 
        xlab("Atrributes") + 
        ggtitle("Female - Before Experiment")

p2 <-  ggplot(data = df_box_pre_plt_m, aes(x = Attribute, y = value, fill = plot_v), color = "#000000") +
        geom_boxplot() +
        scale_x_discrete("Attributes", labels = c("att" = "Attractive", "sin" = "Sincerity", "int" = "Intelligence", "fun" = 
                                                    "Fun", "amb" = "Ambition")) +
        scale_fill_brewer(palette = "Pastel1", name = "Perception", labels = c("Actual Rating", "Self Perception", 
                                                                        "Assumed Perception")) +
        theme_gray(10) +
        theme(legend.title=element_blank()) + 
        ylab("Ratings out of 10") + 
        xlab("Atrributes") + 
        ggtitle("Male - Before Experiment")

p3 <- ggarrange(p1, p2, ncol=2, common.legend = TRUE, legend="bottom")

annotate_figure(p3, top = textGrob("Actual Perception of Others vs Personal Perception",gp=gpar(fontsize=15)))

p4 <-  ggplot(data = df_box_post_plt_f, aes(x = Attribute, y = value, fill = plot_v), color = "#000000") +
        geom_boxplot() +
        scale_x_discrete("Attributes", labels = c("att" = "Attractive", "sin" = "Sincerity", "int" = "Intelligence", "fun" = 
                                                    "Fun", "amb" = "Ambition")) +
        scale_fill_brewer(palette = "Pastel1", name = "Perception", labels = c("Actual Rating", "Self Perception", 
                                                                        "Assumed Perception")) +
        theme_gray(10) +
        theme(legend.title=element_blank()) + 
        ylab("Ratings out of 10") + 
        xlab("Atrributes") + 
        ggtitle("Female - After Experiment")

p5 <-  ggplot(data = df_box_post_plt_m, aes(x = Attribute, y = value, fill = plot_v), color = "#000000") +
        geom_boxplot() +
        scale_x_discrete("Attributes", labels = c("att" = "Attractive", "sin" = "Sincerity", "int" = "Intelligence", "fun" = 
                                                    "Fun", "amb" = "Ambition")) +
        scale_fill_brewer(palette = "Pastel1", name = "Perception", labels = c("Actual Rating", "Self Perception", 
                                                                        "Assumed Perception")) +
        theme_gray(10) +
        theme(legend.title=element_blank()) + 
        ylab("Ratings out of 100") + 
        xlab("Atrributes") + 
        ggtitle("Male - After Experiment")

p6 <- ggarrange(p4, p5, ncol=2, common.legend = TRUE, legend="bottom")

annotate_figure(p6, top = textGrob("Actual Perception of Others vs Personal Perception",gp=gpar(fontsize=15)))
```
